Significance testing with forward stepwise and grouped forward stepwise model selection

### 2013-09-28 paper/paper.tex
More model selection code, more paper editing

\newcommand{\V}{\mathcal{V}}\endlocaldefs
\newcommand{\K}{\mathcal{K}}

@@

\begin{figure}
\begin{center}
\subfigure[Our test]{
\label{fig:lassopvala}
\includegraphics[width=0.5\textwidth]{../figs/small_sim_plot.pdf}}
\hspace{-15pt}
\subfigure[Covariance test]{
\label{fig:lassopvalb}
\includegraphics[width=0.5\textwidth]{../figs/small_sim_plot.pdf}}
\caption{\small \it The left panel shows the empirical distribution
  function of a sample of 20,000 p-values coming
  from a variety of different lasso setups.  The agreement with
  uniform here is excellent.  The right panel shows the empirical
  distribution function of a sample of 10,000 covariance test
  p-values, computed using an $\mathrm{Exp}(1)$ approximation,
  using three different lasso setups.  The
  $\mathrm{Exp}(1)$ approximation is generally conservative.}
\end{center}
\end{figure}

@@

\newpage
We can rewrite this by rationalizing the denominator:
\[
M =
\frac
{ a_h^T b_h +  \sqrt{ a_h^T a_h (1-b_h^Tb_h) + (a_h^T b_h)^2 }  }
{ 1-b_h^Tb_h }
\]
Leaving $M$ in this form we now consider $\lambda_2$. The KKT conditions for the group lasso problem give (directly from Yuan and Lin)
\begin{align*}
\norm{ X_g^T(y - X \beta) } & \leq \lambda w_g \quad \forall \beta_g \neq 0 \\
\beta_g & = \left( 1 - \frac{ \lambda w_g }{ \norm{S_g} } \right)_+ S_g
\end{align*}
where $S_g = X_g^T(y - X \beta_{-g})$. These expressions simplify for $\lambda_2 \leq \lambda < \lambda_1$. Letting $g$ be the index of the first group to enter we now have $S_g = X_g^Ty$ 
\begin{align*}
\beta_g & = \left( 1 - \frac{ \lambda w_g }{ \norm{X_g^Ty} } \right) X_g^Ty \\
\lambda w_h & \geq \norm{ X_h^Ty - X_h^T P_g y (1-\lambda w_g / \norm{X_g^Ty})  } \quad \forall h \neq g
\end{align*}
Now let $\lambda = \lambda_2$, so the inequality above is strict for all other groups and equality is attained for the second group to enter. Hence $\lambda_2$ satisfies
\begin{align*}
\lambda_2 & = \max_{h \neq g} 
\norm{ X_h^T(I - P_g) y - \lambda_2 ( w_g X_h^T P_g y / \norm{X_g^Ty} )  } / w_h\\
& = \max_{h \neq g} \norm{ a_h - \lambda_2 b_h } 
\end{align*}

>>>>

\newcommand{\grad}{\nabla}
\newcommand{\V}{\mathcal{V}}\endlocaldefs
\newcommand{\K}{\mathcal{K}}
\newcommand\tf{\widetilde{f}}

@@

\begin{figure}
\begin{center}
\subfigure[Gaussian design]{
\label{fig:lassopvala}
\includegraphics[width=0.5\textwidth]{../figs/small_sim_gaussian_design.pdf}}
\hspace{-15pt}
\subfigure[Categorical design]{
\label{fig:lassopvalb}
\includegraphics[width=0.5\textwidth]{../figs/small_sim_categorical_design.pdf}}
\caption{\small \it The left panel shows results of a simulation with
  an independent Gaussian design matrix and a signal vector having
  three groups with non-zero coefficients of sizes one, two, and
  three, and seven groups of noise variables with sizes varying from
  one to ten, for a total of 30 variables. For the right panel we
  repeated this setup, but group sizes corresponded to levels of
  categorical variables. The groups of size one were increased to two,
so there are 10 categorical variables with a total of 32 levels.}
\end{center}
\end{figure}

\label{fig:smallselection}

\input{../small_sim_results.tex}

@@

\hrule
\hrule
We can rewrite this by rationalizing the denominator:
\[
M =
\frac
{ a_h^T b_h +  \sqrt{ a_h^T a_h (1-b_h^Tb_h) + (a_h^T b_h)^2 }  }
{ 1-b_h^Tb_h }
\]
Leaving $M$ in this form we now consider $\lambda_2$. The KKT conditions for the group lasso problem give (directly from Yuan and Lin)
\begin{align*}
\norm{ X_g^T(y - X \beta) } & \leq \lambda w_g \quad \forall \beta_g \neq 0 \\
\beta_g & = \left( 1 - \frac{ \lambda w_g }{ \norm{S_g} } \right)_+ S_g
\end{align*}
where $S_g = X_g^T(y - X \beta_{-g})$. These expressions simplify for $\lambda_2 \leq \lambda < \lambda_1$. Letting $g$ be the index of the first group to enter we now have $S_g = X_g^Ty$ 
\begin{align*}
\beta_g & = \left( 1 - \frac{ \lambda w_g }{ \norm{X_g^Ty} } \right) X_g^Ty \\
\lambda w_h & \geq \norm{ X_h^Ty - X_h^T P_g y (1-\lambda w_g / \norm{X_g^Ty})  } \quad \forall h \neq g
\end{align*}
Now let $\lambda = \lambda_2$, so the inequality above is strict for all other groups and equality is attained for the second group to enter. Hence $\lambda_2$ satisfies
\begin{align*}
\lambda_2 & = \max_{h \neq g} 
\norm{ X_h^T(I - P_g) y - \lambda_2 ( w_g X_h^T P_g y / \norm{X_g^Ty} )  } / w_h\\
& = \max_{h \neq g} \norm{ a_h - \lambda_2 b_h } 
\end{align*}
